A Roadmap for\\HEP Software and Computing R\&D\\for the 2020s

### 2018-11-13 CWP/papers/HSF-CWP-2017-01_roadmap/latex/cwp-main.tex
Add reference to CMS plots from ACAT

\begin{figure*}
    \centering
    \begin{subfigure}[b]{0.47\textwidth}
        \includegraphics[width=\textwidth]{cms-cpuHLLHC.pdf}
        \caption{}
        \label{fig:cms-cpu}
    \end{subfigure}
    \quad
    \begin{subfigure}[b]{0.47\textwidth}
        \includegraphics[width=\textwidth]{cms-diskHLLHC.pdf}
        \caption{}
        \label{fig:cms-disk}
    \end{subfigure}
    \caption{CMS estimated CPU (\ref{fig:cms-cpu}) and disk space (\ref{fig:cms-disk})
    resources required into the HL-LHC era, using the current computing model
    with parameters projected out for the next 12 years.}
    \label{fig:cms-resources}
\end{figure*}

>>>>

\begin{figure*}
    \centering
    \begin{subfigure}[b]{0.47\textwidth}
        \includegraphics[width=\textwidth]{cms-cpuHLLHC.pdf}
        \caption{}
        \label{fig:cms-cpu}
    \end{subfigure}
    \quad
    \begin{subfigure}[b]{0.47\textwidth}
        \includegraphics[width=\textwidth]{cms-diskHLLHC.pdf}
        \caption{}
        \label{fig:cms-disk}
    \end{subfigure}
    \caption{CMS estimated CPU (\ref{fig:cms-cpu}) and disk space (\ref{fig:cms-disk})
    resources required into the HL-LHC era, using the current computing model
    with parameters projected out for the next 12 years~\cite{1742-6596-1085-2-022006}.}
    \label{fig:cms-resources}
\end{figure*}
